Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-02-03 manuscript.tex
Fix cost function

Utilizing these metric, a landing site is chosen to minimize the surface cost given as
\begin{align}\label{eq:surface_cost}
    J_l =  J_{\text{distance}} - J_{\text{science}},
\end{align}
subject to a hard inequality constraint requiring that the surface slope is less than a threshold, i.e., \( \phi \leq \phi_m \).

\todo{rewrite the above equation as a function of a candidate landing site location; we also need to describe how many points are considered for minimization; is it just the set of vertices}

>>>>

Utilizing these metrics, a landing site is chosen to minimize the surface cost given as
\begin{align}\label{eq:surface_cost}
    \min_{v_i} J_l(x, v_i) =  J_{\text{distance}}(x, v_i) - J_{\text{science}}(v_i),
\end{align}
subject to a hard inequality constraint requiring that the surface slope is less than a threshold, i.e., \( \phi \leq \phi_m \).
